---
title: "Tutorial"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Tutorial}
  %\VignetteEncoding{UTF-8}
---

Note: Some of the functions in this vignette can be quite demanding.
Increasing the `resolution`, or decreasing the number of
simulations (`N`) may help.
The `cores` argument can extend the computation over multiple cores,
but is only effective on linux machines (including many computing clusters,
such as AstraZeneca's SCP).

```{r, message=FALSE}
library(gonogo)
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)

knitr::opts_chunk$set(fig.width = 7, fig.height = 5)
```


```{r}
ENDPOINTS <- make_endpoints(
  n.domains = 4,
  domain.names = c(
    "Well-being",
    "Biomarker",
    "CT",
    "Ph3"
  ),
  domain.n.vars = c(2, 2, 1, 1),
  corr.inter = 0,
  corr.intra = 0.4,
  vars.sd = c(2, 2, 0.5, 2.1, 1, 5),
  vars.lrv = 0.5,
  vars.tv = 1,
)

ENDPOINTS$vars
ENDPOINTS$sigma
```

# Defining a trial

```{r}
TRIAL <- ENDPOINTS %>%
  with_n_patients(per.group = 17)

power_per_var(TRIAL,
  use.effect = "tv",
  alpha = 0.05
)$vars %>%
  select(name, sigma.sq, df, power)
```

# Defining a policy

```{r}
domain_pol <- p_policy(
  stop.if = for_all_endpoints(p_lalonde %>% is_Stop()),
  go.if   = for_at_least_1_endpoint(p_lalonde %>% is_Go())
)

# This is slow:
# run_montecarlo_grid_schema(
#   TRIAL %at_domain% "Biomarker",
#   domain_pol,
#   list(p.FS = 0.1, p.FG=0.2),
#   resolution=0.05,
#   cores=128) %>% plot_lalonde_grid
```

```{r}
my_policy <- p_policy(
  stop.if =
    ((domain_pol %>% is_Stop()) %at_domain% "Biomarker") %and%
      (for_at_least_k_domains(k = 2, domain_pol %>% is_Stop())
      %at_domains% c("Well-being", "CT", "Ph3")),
  go.if =
    ((domain_pol %>% is_Go()) %at_domain% "Biomarker") %or%
      (for_at_least_k_domains(k = 2, domain_pol %>% is_Go())
      %at_domains% !"Biomarker")
)
```


# Define effects

```{r}
SCENARIO <-
  TRIAL %>%
  with_true_effects(
    go.when = list(
      all.tv = effect_is_gt("tv"),
      Bio.tv = is_gt(0) %and%
        (is_gt("tv") %at_domain% "Biomarker")
    ),
    stop.when = list(
      all.LRV = is_lt("lrv"),
      all.0   = is_lt(0)
    )
  )

SCENARIO %>%
  get_effect_points() %>%
  # Transpose the table so that it fits on the screen
  mutate(across(everything(), as.character)) %>%
  pivot_longer(!"effect.name") %>%
  pivot_wider(names_from = "effect.name", values_from = "value")
```

# Simulate 

```{r}
start_time <- Sys.time()
SIM <-
  SCENARIO %>%
  simulate_with_policy(
    my_policy,
    N = 1000,
    cores = 1,
    simulate.fast = TRUE
  ) %>%
  with_params(list(p.FG = 0.2, p.FS = 0.1)) %>%
  get_decisions_per_effect()
end_time <- Sys.time()
end_time - start_time
SIM %>% select(effect.name, p.go, p.discuss, p.stop, "error.p.overall")
```
# Analyse
```{r}
ggplot(
  SIM %>% pivot_decisions_longer(),
  aes(x = effect.name, y = p, fill = decision)
) +
  geom_col() +
  # Percentage labels
  geom_text(
    aes(label = ifelse(p < 0.08, "", paste0(round(p * 100), "%"))),
    position = position_stack(0.5, reverse = FALSE)
  ) +
  scale_y_continuous(labels = scales::percent) +
  # Lalonde colors
  scale_fill_Decision()
```

# Corrected for multiple testing

```{r}
domain_pol.2 <- p_policy(
  stop.if = for_all_endpoints(p_lalonde %>% is_Stop()),
  go.if = at_least_1_corrected(
    at_each_endpoint(p_lalonde %>% has_go()),
    level = "p.FG",
    correction = "simes"
  )
)

# This is slow:
# run_montecarlo_grid_schema(
#   TRIAL %at_domain% "Biomarker",
#   domain_pol.2,
#   list(p.FS = 0.1, p.FG=0.2),
#   resolution=0.05,
#   cores=128) %>% plot_lalonde_grid
```

```{r}
my_policy.2 <- p_policy(
  stop.if =
    ((domain_pol.2 %>% is_Stop()) %at_domain% "Biomarker") %and%
      (for_at_least_k_domains(k = 2, domain_pol.2 %>% is_Stop())
      %at_domains% c("Well-being", "CT", "Ph3")),
  go.if =
    ((domain_pol.2 %>% is_Go()) %at_domain% "Biomarker") %or%
      (for_at_least_k_domains(k = 2, domain_pol.2 %>% is_Go())
      %at_domains% !"Biomarker")
)

SIM.2 <- SCENARIO %>%
  simulate_with_policy(
    my_policy.2,
    N = 1000,
    cores = 2,
    simulate.fast = TRUE
  ) %>%
  with_params(list(p.FG = 0.2, p.FS = 0.1)) %>%
  get_decisions_per_effect()

ggplot(
  SIM.2 %>% pivot_decisions_longer(),
  aes(x = effect.name, y = p, fill = decision)
) +
  geom_col() +
  # Percentage labels
  geom_text(
    aes(label = ifelse(p < 0.08, "", paste0(round(p * 100), "%"))),
    position = position_stack(0.5, reverse = FALSE)
  ) +
  scale_y_continuous(labels = scales::percent) +
  # Lalonde colors
  scale_fill_Decision()
```
