---
title: "Figures concerning rates"
output:
  pdf_document:
    latex_engine: xelatex
---


```{r, results= "hide", message=F, warning=F}
library(gonogo)
library(tikzDevice)
source("config.R")
options(tikzLatexPackages = c(
  "\\usepackage{tikz}\n",
  "\\usepackage[active,tightpage,psfixbb]{preview}\n",
  "\\PreviewEnvironment{pgfpicture}\n",
  "\\setlength\\PreviewBorder{0pt}\n",
  "\\usepackage{ulem}\n",
  "\\newcommand{\\downcone}{m}\n",
  "\\newcommand{\\upcone}{m}\n",
  "\\newcommand{\\vLRV}{LRV}\n",
  "\\newcommand{\\vTV}{TV}\n",
  "\\newcommand{\\vNoEffect}{0}\n",
  "\\newcommand{\\RFStop}{\\Theta^{FS}}\n",
  paste0(
    "\\newcommand{\\G",
    c("Ind", "IndAdj", "Hot", "Lik", "LikAdj", "Meas", "IndBon"),
    "}{mmmmm}"
  )
))
options(
  tikzDocumentDeclaration =
    "\\documentclass[10pt,onecolumn,english]{book}"
)
```

```{r}
system(paste("echo '", gonogo_version(), "'"))
```

```{r}
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
options(dplyr.summarise.inform = FALSE)
library(latex2exp)
library(kableExtra)
```

```{r}
TRIAL <- list()
for (n.per.group in c(17)) {
  for (domain.n.vars in c(2, 3, 4)) {
    for (corr.intra in (c(0, 0.4, 0.8))) {
      TRIAL[[paste0("V=", domain.n.vars, ".ρ=(", corr.intra, ")", ".N=", n.per.group)]] <-
        make_endpoints(
          n.domains = 1,
          domain.n.vars = domain.n.vars,
          corr.intra = corr.intra
        ) %>% with_n_patients(per.group = n.per.group)
    }
  }
}

power_per_var(TRIAL$`V=2.ρ=(0).N=17`, use.effect = "tv")
power_per_var(TRIAL$`V=2.ρ=(0).N=27`, use.effect = "tv-lrv", alpha = 0.1)


for (domain.n.vars in c(2, 3, 4)) {
  for (corr.intra in (c(0, 0.4, 0.8))) {
    n.low.pow <- 1
    TRIAL[[paste0("V=", domain.n.vars, ".ρ=(", corr.intra, ")", ".N=17.mixed")]] <-
      make_endpoints(
        n.domains = 1,
        domain.n.vars = domain.n.vars,
        vars.sd = c(
          rep(1, domain.n.vars - n.low.pow),
          rep(2, n.low.pow)
        ),
        corr.intra = corr.intra
      ) %>% with_n_patients(per.group = 17)
  }
}

power_per_var(TRIAL$`V=3.ρ=(0).N=17.mixed`, use.effect = "tv")
```

```{r}
POLICY <- list(
  uni = p_policy(
    stop.if   = for_all_endpoints(p_univariate %>% is_Stop()),
    go.if     = for_at_least_1_endpoint(p_univariate %>% is_Go())
  ),
  uni.adj =
    p_policy(
      stop.if = for_all_endpoints(p_univariate %>% has_stop()),
      go.if =
        at_least_1_adjusted(
          at_each_endpoint(p_univariate %>% has_go()),
          correction = "simes"
        )
    ),
  uni.bon =
    p_policy(
      stop.if = for_all_endpoints(p_univariate %>% has_stop()),
      go.if =
        at_least_1_adjusted(
          at_each_endpoint(p_univariate %>% has_go()),
          correction = "bonferroni"
        )
    ),
  hot = p_hotelling(
    false.stop = for_at_least_1_endpoint(effect_is_gt("tv")),
    false.go   = for_all_endpoints(effect_is_lt("lrv"))
  ),
  lik = p_likelihood(
    false.stop = for_at_least_1_endpoint(effect_is_gt("tv")),
    false.go   = for_all_endpoints(effect_is_lt("lrv"))
  ),
  meas = p_measure(
    false.stop = for_at_least_1_endpoint(is_gt("tv")),
    false.go   = for_all_endpoints(effect_is_lt("lrv"))
  ),
  lik.adj =
    p_likelihood_adj(
      false.stop = for_at_least_1_endpoint(effect_is_gt("tv")),
      false.go   = for_all_endpoints(effect_is_lt("lrv")),
      df.go      = "max",
      df.stop    = 1
    )
)
```

```{r}
go.regions <- list( # theta.fs = effect_is_gt("tv"),
  go.A = effect_is_gt("tv"),
  go.B = for_at_least_1_endpoint(effect_is_gt("tv")) %and%
    for_all_endpoints(effect_is_gt(0))
)
stop.regions <- list( # theta.fg = effect_is_lt("lrv"),
  stop.A = effect_is_lt("lrv"),
  stop.B1 = for_all_endpoints(effect_is_lt("lrv")) %and%
    for_at_least_all_but_1_endpoint(effect_is_lt("0")),
  stop.B2 = for_all_endpoints(effect_is_lt("lrv")) %and%
    for_at_least_half_of_endpoints(effect_is_lt("0")),
  stop.C = effect_is_lt(0)
)

DEFAULT.PARAMS <- list("p.FS" = 0.1, "p.FG" = 0.2)
```

```{r}
SCENARIO <- lapply(TRIAL, function(trial) {
  make_scenario(
    trial = trial,
    go.regions = go.regions,
    stop.regions = stop.regions
  ) %>% expand_regions()
})
```

```{r}
SCENARIO$`V=2.ρ=(0).N=17`$region.points
SCENARIO$`V=3.ρ=(0.4).N=17`$region.points
SCENARIO$`V=4.ρ=(0.8).N=27`$region.points
SCENARIO$`V=4.ρ=(0.8).N=17.mixed`$region.points
```
```{r}
sim23 <- SCENARIO$`V=2.ρ=(0).N=17` %>% simulate_with_policies(list(POLICY$lik.adj, POLICY$uni.adj))
sim2 <- sim23[[1]]
sim3 <- sim23[[2]]
```

```{r}
# policy <- schema %>% instantiate_at(scenario$trial$endpoints)
SCENARIO.SIM <- function(scenario.name, policy.name) {
  scenario <- SCENARIO[[scenario.name]]
  policy.schema <- POLICY[[policy.name]]
  if (any(stringr::str_detect(policy.name, c("meas"))) &&
    (stringr::str_detect(scenario.name, "N=27") ||
      stringr::str_detect(scenario.name, "\\.mixed"))) {
    return(NULL)
  }
  sim.name <- paste0(scenario.name, ".", policy.name)
  system(paste0("echo '", sim.name, "'"))
  run_experiment_inline(
    paste0("sim_20220311_1004", "_", sim.name),
    function(N, cores, splits) {
      scenario %>%
        simulate_with_policy(policy.schema,
          N = N,
          cores = cores,
          splits = splits,
          verbose = TRUE
        )
    },
    N = 10000, cores = 1, splits = 1,
    # quick.test = function(f) f(N = 5, cores = 1,splits=1),
    depend.on.function = FALSE,
    depends.on = list(scenario.name, policy.name),
    random.seed = 202203071715 %% .Machine$integer.max
  )
}
```


```{r}
library(doParallel)
stopImplicitCluster()
options(mc.cores = 16, cores = 16)
registerDoParallel(makeForkCluster())

SCENARIO.METRICS <-
  foreach(scenario.name = names(SCENARIO), .combine = "bind_rows") %:%
  foreach(policy.name = names(POLICY), .combine = "bind_rows") %dopar%
  {
    sim.name <- paste0(scenario.name, ".", policy.name)
    sim <- SCENARIO.SIM(scenario.name, policy.name)
    if (is.null(sim)) {
      return(NULL)
    }
    PARAMS <- list(
      default = DEFAULT.PARAMS
    )
    lapply(names(PARAMS), function(params.name) {
      params <- PARAMS[[params.name]]
      sim.with.params <- sim %>% with_params(params)
      sim.with.params %>%
        four_metrics_all() %>%
        mutate(
          scenario = !!scenario.name,
          policy = !!policy.name,
          params = !!params.name,
          .before = everything()
        )
    }) %>% bind_rows()
  } %>%
  arrange(params)

SCENARIO.METRICS <- SCENARIO.METRICS %>%
  mutate(
    scenario.vars = stringr::str_match(scenario, "V=([0-9]*)\\.")[, 2],
    scenario.corr = stringr::str_match(scenario, "ρ=\\(([0-9.]*)\\)")[, 2],
    scenario.N = stringr::str_match(scenario, "N=([0-9]*)")[, 2],
    scenario.mixed = stringr::str_detect(scenario, "\\.mixed"),
    .before = everything()
  )

print(max(
  SCENARIO.METRICS$error.go.A,
  SCENARIO.METRICS$error.go.B,
  SCENARIO.METRICS$error.stop.A,
  SCENARIO.METRICS$error.stop.B1,
  SCENARIO.METRICS$error.stop.B2
))

SCENARIO.METRICS
```
  
# Table 3.3 - Comparison of unadjusted multivariate policies.

```{r} 
options(knitr.table.format = "latex")
# library(knitr)
library(kableExtra)

format_round <- function(x, digits) format(round(x, digits), nsmall = digits)

for (scenario.N in c(17)) {
  # for(scenario.vars in unique(SCENARIO.METRICS$scenario.vars)){
  for (params in c("default")) {
    df <- SCENARIO.METRICS %>%
      # filter(scenario.vars == !!scenario.vars) %>%
      filter(scenario.N == !!scenario.N) %>%
      filter(!scenario.mixed) %>%
      filter(params == "default") %>%
      filter(policy %in% c("uni", "meas", "hot")) %>%
      arrange(scenario.vars, list(
        uni = 1,
        uni.bon = 6,
        uni.adj = 7,
        hot = 2,
        meas = 3,
        lik = 4,
        lik.adj = 8
      )[policy], scenario.corr) %>%
      transmute(
        Policy = policy,
        "$ρ$" = paste0("", scenario.corr, ""),
        FSR = round(FSR.go.B, 2),
        CGr = round(CGr.go.B, 2),
        FGr = round(FGr.stop.B1, 2),
        CSr = round(CSr.stop.B1, 2),
        .CGr.TV = round(CGr.go.A, 2),
        "CGr "   = .CGr.TV,
        .FGR.LRV = round(FGR.stop.A, 2),
        "FGR "   = .FGR.LRV,
        .CSr.0  = round(CSr.stop.C, 2),
        "CSr " = .CSr.0,
        .policy = policy,
        .scenario.corr = scenario.corr,
        .scenario.vars = scenario.vars,
      ) %>%
      group_by(.scenario.corr, .scenario.vars) %>%
      mutate(
        .CGr.is.max = (CGr == max(CGr)),
        .CSr.is.max = (CSr == max(CSr)),
        .FGr.is.min = (FGr == min(FGr)),
        .FSR.is.min = (FSR == min(FSR)),
        .CGr.TV.is.max = (.CGr.TV == max(.CGr.TV)),
        .FGR.LRV.is.min = (.FGR.LRV == min(.FGR.LRV)),
        .CSr.0.is.max = (.CSr.0 == max(.CSr.0)),
      ) %>%
      ungroup()


    table <- kbl(df %>%
      mutate(
        CGr = cell_spec(format_round(CGr, 2), bold = .CGr.is.max, format = "latex"),
        CSr = cell_spec(format_round(CSr, 2), bold = .CSr.is.max, format = "latex"),
        FGr = cell_spec(format_round(FGr, 2), bold = .FGr.is.min, format = "latex"),
        FSR = cell_spec(format_round(FSR, 2), bold = .FSR.is.min, format = "latex"),
        "CGr " = cell_spec(format_round(.CGr.TV, 2), bold = .CGr.TV.is.max, format = "latex"),
        "FGR " = cell_spec(format_round(.FGR.LRV, 2), bold = .FGR.LRV.is.min, format = "latex"),
        "CSr " = cell_spec(format_round(.CSr.0, 2), bold = .CSr.0.is.max, format = "latex"),
        Policy = list(
          uni = "$\\GInd$",
          uni.adj = "$\\GIndAdj$",
          uni.bon = "$\\GIndBon$",
          hot = "$\\GHot$",
          meas = "$\\GMeas$",
          lik = "$\\GLik$",
          lik.adj = "$\\GLikAdj$"
        )[.policy]
      ) %>%
      select(!starts_with(".")) %>% rename(" " = Policy),
    "latex",
    booktabs = T, escape = FALSE
    )

    for (scenario.vars in unique(df$.scenario.vars)) {
      table <- table %>% pack_rows(
        paste0("V=", scenario.vars),
        min(which(df$.scenario.vars == scenario.vars)),
        max(which(df$.scenario.vars == scenario.vars))
      )
    }
    table <- table %>% collapse_rows(columns = 1, latex_hline = "major")
    table <- table %>% add_header_above(c(
      " " = 2, # "Parameters"=0,
      "$\\\\RFStop = \\\\RCGoExt$" = 2, "$\\\\RCStopExt$" = 2,
      "$\\\\upcone{\\\\vTV}$" = 1, "$\\\\downcone{\\\\vLRV}$" = 1, "$\\\\downcone{\\\\vct{0}}$" = 1
    ), escape = F)
    table <- table %>% kable_styling(
      latex_options = "striped", position = "left",
      stripe_index = which(df$.scenario.corr != 0.4)
    )
    file.name <- paste0("report/table_measure_all_", params, "_", scenario.N, ".tex")
    table %>% save_kable(file = file.name)
    cat(paste0(readLines(file.name)[1:7] %>% .[!is.na(.)], collapse = "\n"))
  }
}
```


# Table 3.5 - Comparison of adjusted policies
(table_measure_ext_default_17.tex)
# Table 3.6 - Comparison of selected adjusted policies in the presence of one underpowered variable.
(table_measure_ext_default_17.tex)

```{r} 
options(knitr.table.format = "latex")
# library(knitr)
library(kableExtra)

format_round <- function(x, digits) format(round(x, digits), nsmall = digits)

the.scenario.N <- c(17, 17)
the.scenario.mixed <- c(FALSE, TRUE)
the.include.half <- c(TRUE, FALSE)

for (i in seq(length(the.scenario.N))) {
  # for(scenario.vars in unique(SCENARIO.METRICS$scenario.vars)){
  scenario.N <- the.scenario.N[i]
  scenario.mixed <- the.scenario.mixed[i]
  include.half <- the.include.half[i]
  for (params in c("default")) {
    df <- SCENARIO.METRICS %>%
      # filter(scenario.vars == !!scenario.vars) %>%
      filter(scenario.N == !!scenario.N) %>%
      filter(scenario.mixed == !!scenario.mixed) %>%
      filter(params == "default") %>%
      filter(policy %in% c("uni.bon", "uni.adj", "lik.adj") |
        include.half & policy == "lik") %>%
      arrange(scenario.vars, list(
        uni = 1,
        uni.bon = 0.5,
        uni.adj = 2,
        hot = 2,
        meas = 3,
        lik = 4,
        lik.adj = 5
      )[policy], scenario.corr) %>%
      transmute(
        Policy = policy,
        "$ρ$" = paste0("", scenario.corr, ""),
        # "$\\pFS$" = round(params.p.FS,4),
        # "$\\pFG$" = round(params.p.FG,4),
        FSR = round(FSR.go.B, 2),
        CGr = round(CGr.go.B, 2),
        FGr = round(FGr.stop.B1, 2),
        # FGR = round(FGR.stop.B1,2),
        CSr = round(CSr.stop.B1, 2),
        # "FSr " = round(FSr.go.A,2),
        .CGr.TV = round(CGr.go.A, 2),
        "CGr "   = .CGr.TV,
        .FGR.LRV = round(FGR.stop.A, 2),
        "FGR "   = .FGR.LRV,
        # "FGr " = round(FGr.stop.A,2),
        # "CSr " = round(CSr.stop.A,2),
        # "FGr  " = round(FGr.stop.C,2),
        .CSr.0  = round(CSr.stop.C, 2),
        "CSr " = .CSr.0,
        .policy = policy,
        .scenario.corr = scenario.corr,
        .scenario.vars = scenario.vars,
      ) %>%
      group_by(.scenario.corr, .scenario.vars) %>%
      mutate(
        .CGr.is.max = (CGr == max(CGr)),
        .CSr.is.max = (CSr == max(CSr)),
        .FGr.is.min = (FGr == min(FGr)),
        .FSR.is.min = (FSR == min(FSR)),
        .CGr.TV.is.max = (.CGr.TV == max(.CGr.TV)),
        .FGR.LRV.is.min = (.FGR.LRV == min(.FGR.LRV)),
        .CSr.0.is.max = (.CSr.0 == max(.CSr.0)),
      ) %>%
      ungroup()


    table <- kbl(df %>%
      mutate(
        CGr = cell_spec(format_round(CGr, 2), bold = .CGr.is.max, format = "latex"),
        CSr = cell_spec(format_round(CSr, 2), bold = .CSr.is.max, format = "latex"),
        FGr = cell_spec(format_round(FGr, 2), bold = .FGr.is.min, format = "latex"),
        FSR = cell_spec(format_round(FSR, 2), bold = .FSR.is.min, format = "latex"),
        "CGr " = cell_spec(format_round(.CGr.TV, 2), bold = .CGr.TV.is.max, format = "latex"),
        "FGR " = cell_spec(format_round(.FGR.LRV, 2), bold = .FGR.LRV.is.min, format = "latex"),
        "CSr " = cell_spec(format_round(.CSr.0, 2), bold = .CSr.0.is.max, format = "latex"),
        Policy = list(
          uni = "$\\GInd$",
          uni.adj = "$\\GIndAdj$",
          uni.bon = "$\\GIndBon$",
          hot = "$\\GHot$",
          meas = "$\\GMeas$",
          lik = "$\\GLik$",
          lik.adj = "$\\GLikAdj$"
        )[.policy]
      ) %>%
      select(!starts_with(".")) %>% rename(" " = Policy),
    "latex",
    booktabs = T, escape = FALSE
    )

    for (scenario.vars in unique(df$.scenario.vars)) {
      table <- table %>% pack_rows(
        paste0("V=", scenario.vars),
        min(which(df$.scenario.vars == scenario.vars)),
        max(which(df$.scenario.vars == scenario.vars))
      )
    }
    table <- table %>% collapse_rows(columns = 1, latex_hline = "major")
    table <- table %>% add_header_above(c(
      " " = 2, # "Parameters"=0,
      "$\\\\RFStop = \\\\RCGoExt$" = 2, "$\\\\RCStopExt$" = 2,
      "$\\\\upcone{\\\\vTV}$" = 1, "$\\\\downcone{\\\\vLRV}$" = 1, "$\\\\downcone{\\\\vct{0}}$" = 1
    ), escape = F)
    table <- table %>% kable_styling(
      latex_options = "striped", position = "left",
      stripe_index = which(df$.scenario.corr != 0.4)
    )
    file.name <- paste0(
      "report/table_measure_ext_",
      params,
      "_", scenario.N,
      ifelse(scenario.mixed, "_mixed", ""),
      ".tex"
    )
    table %>% save_kable(file = file.name)
    cat(paste0(readLines(file.name)[1:7] %>% .[!is.na(.)], collapse = "\n"))
  }
}
```


# Figure 3.3 - Comparison of selected metrics for all policies under consideration for a single domain
(plot_FGR_FSR_all_start.tex.fig)
# Figure 3.5 - Comparison of Go rates for the adjusted policies, for a single domain.
(plot_FGR_FSR_all_end.tex.fig)

```{r, fig.height = 9, fig.width=8}
source("theme_pub.R")
library(forcats)
dd <- SCENARIO.METRICS %>%
  pivot_longer(cols = matches("[FC][GS][Rr].(go|stop).[A-Z][0-9]*"), names_to = "metric") %>%
  filter(scenario.N == 17 & scenario.mixed == FALSE |
    # scenario.N == 27 & scenario.mixed == FALSE |
    scenario.N == 17 & scenario.mixed == TRUE) %>%
  filter(`scenario.corr` <= 0.4) %>%
  filter( # policy %in% c("hot","uni","meas")
  ) %>%
  mutate(combo = paste(scenario.N, scenario.mixed, sep = ".")) %>%
  mutate(combo = factor(combo, levels = c("17.FALSE", "17.TRUE", "27.FALSE"))) %>%
  # mutate(metric = factor(metric, levels=c("FGR.stop.A","FSR.go.B"))) %>%
  mutate(policy = factor(policy, levels = c(
    "uni", "meas", "hot", "lik",
    "uni.bon", "uni.adj", "lik.adj"
  )))

policy_labels <- c(
  "uni" = "$\\GInd$ ",
  "meas" = "$\\GMeas$ ",
  "hot" = "$\\GHot$ ",
  "uni.bon" = "$\\GIndBon$",
  "uni.adj" = "$\\GIndAdj$",
  "lik" = "$\\GLik$",
  "lik.adj" = "$\\GLikAdj$"
)
dd1 <- dd %>%
  mutate(metric = factor(metric, levels = c("CSr.stop.C", "FSR.go.B", "FGR.stop.A"))) %>%
  filter(!is.na(metric)) %>%
  filter(combo == "17.FALSE") %>%
  mutate(combo = paste(combo, scenario.corr, sep = "_")) %>%
  mutate(combo = factor(combo, levels = c("17.FALSE_0", "17.FALSE_0.4")))
gg <- ggplot(dd1) +
  geom_rect(
    data = dd1 %>% select(metric, combo) %>% distinct(),
    aes(
      xmin = -Inf, xmax = +Inf,
      ymin = -Inf, ymax = +Inf,
      fill = list(
        `FGR.stop.A` = DECISION$Discuss,
        `FSR.go.B` = DECISION$Discuss,
        `CSr.stop.C` = DECISION$Stop
      )[as.character(metric)] %>% unlist()
    ), alpha = .05
  ) +
  geom_jitter(aes(color = policy, x = scenario.vars, y = value, shape = scenario.corr), height = 0, width = 0.1) +
  facet_grid(metric ~ combo,
    scales = "free_y",
    labeller = labeller(
      combo = c(
        `17.FALSE_0` = "$N=17$, $\\sigma_V=1$, $\\rho=0$",
        `17.FALSE_0.4` = "$N=17$, $\\sigma_V=1$, $\\rho=0.4$"
      ),
      metric = c(
        `FGR.stop.A` = "FGR at $\\downcone{\\vLRV}$",
        `FSR.go.B` = "FSR at $\\RFStop (= R^{\\mathrm{Go}}_{\\mathrm{ext}})$",
        `CSr.stop.C` = "CSr at $\\downcone{\\vNoEffect}$"
      )
    )
  ) +
  theme_Publication() +
  scale_fill_Decision(guide = "none") +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  geom_hline(data = tibble(
    metric = c("FSR.go.B", "FGR.stop.A"),
    yintercept = c(0.1, 0.2)
  ), aes(yintercept = yintercept)) +
  scale_colour_Publication(labels = policy_labels, drop = F) +
  scale_y_continuous(labels = scales::label_percent(suffix = "\\%")) +
  scale_shape_Publication() +
  labs(x = "Number of variables ($V$)", y = "", colour = "Policy", shape = "$\\rho$") +
  guides(color = guide_legend(nrow = 2, byrow = TRUE))
print(gg)
file.name <- "report/plot_FGR_FSR_all_start.tex.fig"
tikzDevice::tikz(
  file = file.name,
  width = 4.7, height = 7
)
print(gg)
dev.off()

dd2 <- dd %>%
  mutate(metric = factor(metric, levels = c("FGR.stop.A", "CGr.go.A", "CGr.go.B"))) %>%
  filter(!is.na(metric)) %>%
  filter(policy %in% c("uni.bon", "uni.adj", "lik.adj"))
gg <- ggplot(dd2) +
  geom_rect(
    data = dd2 %>% select(metric, combo) %>% distinct(),
    aes(
      xmin = -Inf, xmax = +Inf,
      ymin = -Inf, ymax = +Inf,
      fill = dplyr::if_else(metric == "FGR.stop.A", DECISION$Discuss, DECISION$Go)
    ), alpha = .05
  ) +
  geom_jitter(aes(color = policy, x = scenario.vars, y = value, shape = scenario.corr), height = 0, width = 0.1) +
  facet_grid(metric ~ combo,
    scales = "free_y",
    labeller =
      labeller(
        combo = c(
          `17.FALSE` = "$N=17$, $\\sigma_V=1$",
          `17.TRUE` = "$N=17$, $\\sigma_V=2$",
          `27.FALSE` = "$N=27$, $\\sigma_V=1$"
        ),
        metric = c(
          `FGR.stop.A` = "FGR at $\\downcone{\\vLRV}$",
          `CGr.go.A` = "CGr at $\\upcone{\\vTV}$",
          `CGr.go.B` = "CGr at $R^{\\mathrm{Go}}_{\\mathrm{ext}} (= \\RFStop)$"
        )
      )
  ) +
  scale_fill_Decision(guide = "none") +
  theme_Publication() +
  theme(legend.position = "bottom", legend.box = "vertical", legend.margin = margin()) +
  geom_hline(data = tibble(
    metric = c("FGR.stop.A"),
    yintercept = c(0.2)
  ), aes(yintercept = yintercept)) +
  scale_colour_Publication(labels = policy_labels[levels(droplevels(dd2$policy))], drop = F, breaks = levels(droplevels(dd2$policy))) +
  scale_y_continuous(labels = scales::label_percent(suffix = "\\%")) +
  scale_shape_Publication() +
  labs(x = "Number of variables ($V$)", y = "", shape = "$\\rho$", colour = "Policy")
print(gg)
file.name <- "report/plot_FGR_FSR_all_end.tex.fig"
tikzDevice::tikz(
  file = file.name,
  width = 4.7, height = 7.5
)
print(gg)
dev.off()
```




