---
title: "Figures concerning rates"
output:
  pdf_document:
    latex_engine: xelatex
---


```{r, results= "hide", message=F, warning=F}
library(gonogo)
library(tikzDevice)
# devtools::load_all()
source("config.R")
options(tikzLatexPackages = c(
  getOption("tikzLatexPackages"),
  "\\usepackage{ulem}"
))
```

```{r}
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
options(dplyr.summarise.inform = FALSE)
library(latex2exp)
library(kableExtra)
```
```{r}
system(paste("echo '", gonogo_version(), "'"))
```

```{r}
low.power.sd <- 2
TRIAL <- list()
for (n.per.group in c(17)) {
  for (n.domains in c(1, 2, 3, 4, 5)) {
    # Maximum 10 variables, 4 variables per domain
    for (n.vars in seq(n.domains, min(4 * n.domains, 9))) {
      # We skip these ones to save some computation
      for (domain.n.vars in generate_variable_groupings(
        n.domains,
        n.vars,
        min.vars.per.domain = 1,
        max.vars.per.domain = 4,
        ordered.except.for.first = 1
      )) {
        for (corr.intra in (c(0.4))) {
          for (corr.inter in (c(0, 0.2, 0.4))) {
            TRIAL[[paste0(
              "D=", n.domains,
              ".V=", n.vars,
              ".Vd=", paste(domain.n.vars, collapse = "_"),
              ".ρ=(", corr.intra, ")",
              ".τ=(", corr.inter, ")",
              ".N=", n.per.group,
              ".extra=none"
            )]] <-
              make_endpoints(
                n.domains = n.domains,
                domain.n.vars = domain.n.vars,
                corr.intra = corr.intra,
                corr.inter = corr.inter
              ) %>% with_n_patients(per.group = n.per.group)

            if (domain.n.vars[1] < 4) {
              TRIAL[[paste0(
                "D=", n.domains,
                ".V=", n.vars,
                ".Vd=", paste(domain.n.vars, collapse = "_"),
                ".ρ=(", corr.intra, ")",
                ".τ=(", corr.inter, ")",
                ".N=", n.per.group,
                ".extra=in_first_domain"
              )]] <-
                make_endpoints(
                  n.domains = n.domains,
                  domain.n.vars = {
                    dnv <- domain.n.vars
                    dnv[1] <- dnv[1] + 1
                    dnv
                  },
                  vars.sd = c(
                    rep(1, length.out = domain.n.vars[1]),
                    2,
                    rep(1, length.out = sum(domain.n.vars) - domain.n.vars[1])
                  ),
                  corr.intra = corr.intra,
                  corr.inter = corr.inter
                ) %>% with_n_patients(per.group = n.per.group)
            }

            if (n.domains < 5) {
              TRIAL[[paste0(
                "D=", n.domains,
                ".V=", n.vars,
                ".Vd=", paste(domain.n.vars, collapse = "_"),
                ".ρ=(", corr.intra, ")",
                ".τ=(", corr.inter, ")",
                ".N=", n.per.group,
                ".extra=in_own_domain"
              )]] <-
                make_endpoints(
                  n.domains = n.domains + 1,
                  domain.n.vars = c(domain.n.vars, 1),
                  vars.sd = c(rep(1, length.out = sum(domain.n.vars)), 2),
                  corr.intra = corr.intra,
                  corr.inter = corr.inter
                ) %>% with_n_patients(per.group = n.per.group)
            }
          }
        }
      }
    }
  }
}

parse_dot_name <- function(name) {
  res <- stringr::str_match_all(name, "(([^.=]+)=([^().=]+|\\(([^)]+)\\)))*")[[1]]
  ii <- !is.na(res[, 3])
  res <- structure(
    coalesce(res[ii, 5], res[ii, 4]),
    names = res[ii, 3]
  ) %>% as.list()
  res <- lapply(res, function(v) {
    # if(stringr::str_detect(v, "^([0-9.]+_)*[0-9.]+$")) {
    if (stringr::str_detect(v, "^[0-9.]+$")) {
      n <- as.numeric(stringr::str_split(v, "_", simplify = TRUE))
      # if(length(n) > 1) list(n) else n
      n
    } else {
      v
    }
  }) %>% as_tibble_row()
  res$Vd <- as.character(res$Vd)
  res
}
bind_rows(lapply(names(TRIAL), function(x) {
  bind_cols(
    tibble_row(trial.name = x),
    parse_dot_name(x)
  )
}))
```

```{r}

uni_adj <- make_schema_alias("uni_adj")
dealias.uni_adj <- function(...) {
  p_policy(
    stop.if = for_all_endpoints(p_univariate %>% has_stop()),
    go.if =
      at_least_1_adjusted(
        at_each_endpoint(p_univariate %>% has_go()),
        correction = "simes"
      )
  )
}

uni_adj_extra <- make_schema_alias("uni_adj_extra")
dealias.uni_adj_extra <- function(...) {
  p_policy(
    stop.if = (uni_adj %>% has_stop() %>%
      at_selected_vars(all_but_last_var)) %or%
      (p_not(uni_adj %>% has_go() %>%
        at_selected_vars(all_but_last_var)) %and%
        (p_univariate %>% has_stop() %>% at_selected_vars(last_var))),
    go.if = ((uni_adj %>% has_go()) %>%
      at_selected_vars(all_but_last_var)) %or%
      (p_univariate %>% has_go() %>% at_selected_vars(last_var))
  )
}


uni_adj_only_stop <- make_schema_alias("uni_adj_only_stop")
dealias.uni_adj_only_stop <- function(...) {
  p_policy(
    stop.if = (uni_adj %>% has_stop() %>%
      at_selected_vars(all_but_last_var)) %or%
      (p_not(uni_adj %>% has_go() %>%
        at_selected_vars(all_but_last_var)) %and%
        (p_univariate %>% has_stop() %>% at_selected_vars(last_var))),
    go.if = (uni_adj %>% has_go()) %>%
      at_selected_vars(all_but_last_var)
  )
}

POLICY <- list(
  uni_adj = uni_adj,
  uni_adj_extra = uni_adj_extra,
  all_domains_equal =
    p_policy(
      stop.if =
        at_most_k(k = "z", at_each_domain(uni_adj %>% is_Go())) %or%
          p_all(at_each_domain(uni_adj %>% is_Stop())),
      go.if =
        (at_least_k(k = "x", at_each_domain(uni_adj %>% is_Go())) %or%
          p_all(at_each_domain(uni_adj %>% is_Go()))) %and%
          none_of(at_each_endpoint(is_negatively_significant))
    ),
  hierarchical_domains =
    p_policy(
      stop.if =
        ((uni_adj %>% is_Stop()) %at_domain% "d1") %and%
          # 2 of the other domains are stop (3 including the first one)
          at_least_k(k = 1 + 2, at_each_domain(uni_adj %>% is_Stop())),
      go.if =
        (((uni_adj %>% is_Go()) %at_domain% "d1") %or%
          # x of the other domains ~ x of all domains (otherwise the first condition holds)
          at_least_k(k = "x", at_each_domain(uni_adj %>% is_Go()))) %and%
          none_of(at_each_endpoint(is_negatively_significant))
    )
)

for (schema.name in c("uni_adj", "uni_adj_extra", "uni_adj_only_stop")) {
  schema <- make_schema_alias(schema.name)
  POLICY[[paste0("all_domains_equal.", schema.name)]] <-
    p_policy(
      stop.if = at_most_k_of(
        k = "z",
        (schema %>% is_Go()) %at_domain% "d1",
        at_each_domain(uni_adj %>% is_Go()) %at_domains% (!"d1")
      ) %or%
        p_all_of(
          (schema %>% is_Stop()) %at_domain% "d1",
          at_each_domain(uni_adj %>% is_Stop()) %at_domains% (!"d1")
        ),
      go.if =
        (at_least_k_of(
          k = "x",
          (schema %>% is_Go()) %at_domain% "d1",
          at_each_domain(uni_adj %>% is_Go()) %at_domains% (!"d1")
        ) %or%
          p_all_of(
            (schema %>% is_Go()) %at_domain% "d1",
            at_each_domain(uni_adj %>% is_Go()) %at_domains% (!"d1")
          ))
        %and%
          none_of(at_each_endpoint(is_negatively_significant))
    )

  POLICY[[paste0("hierarchical_domains.", schema.name)]] <-
    p_policy(
      stop.if =
        ((schema %>% is_Stop()) %at_domain% "d1") %and%
          # 2 of the other domains are stop (3 including the first one)
          (at_least_k(k = 2, at_each_domain(uni_adj %>% is_Stop())) %at_domains% (!"d1")),
      go.if =
        (((schema %>% is_Go()) %at_domain% "d1") %or%
          # x of the other domains ~ x of all domains (otherwise the first condition holds)
          (at_least_k(k = "x", at_each_domain(uni_adj %>% is_Go())) %at_domains% (!"d1")))
        %and% none_of(at_each_endpoint(is_negatively_significant))
    )
}
```

```{r}
go.regions <- list(
  go.A = effect_is_gt("tv"),
  go.B = (effect_is_gt("tv") %or% at_least_k(
    k = 2,
    at_each_domain(effect_is_gt("tv"))
  )) %and%
    for_all_endpoints(effect_is_gt(0)),
  go.C = (at_least_k(k = 2, at_each_domain(effect_is_gt("tv"))) %or% effect_is_gt("tv")) %and%
    for_all_endpoints(effect_is_gt(0)) %and%
    (effect_is_gt("tv") %at_domain% "d1")
)
stop.regions <- list(
  stop.A = effect_is_lt("lrv"),
  stop.C = effect_is_lt(0),
  stop.H = for_all_endpoints(effect_is_lt("lrv")) %and%
    (at_least_k(k = 2, at_each_domain(effect_is_lt(0))) %or% effect_is_lt(0)) %and%
    (effect_is_lt("0") %at_domain% "d1")
)

DEFAULT.PARAMS <- list(
  "p.FS" = 0.1, "p.FG" = 0.2, "alpha" = 0.05,
  "x" = 2, "z" = 0
)
```

```{r}
GET.SCENARIO <- function(trial.name) {
  trial <- TRIAL[[trial.name]]
  make_scenario(
    trial = trial,
    go.regions = go.regions,
    stop.regions = stop.regions
  ) %>% expand_regions()
}
# for(scenario.name in names(TRIAL)) {
#   message(scenario.name)
#   GET.SCENARIO(scenario.name)
# }
```

```{r}
GET.SIM <- function(scenario.name, policy.name) {
  # if(n_domains(TRIAL[[scenario.name]]) <= 1) { return(NULL)  }
  scenario <- GET.SCENARIO(scenario.name)
  policy.schema <- POLICY[[policy.name]]
  sim <- run_experiment_inline(paste0(
    "sim_20220225_1436",
    "_",
    scenario.name,
    "_",
    policy.name
  ),
  function(N, cores, splits) {
    scenario %>%
      simulate_with_policy(policy.schema,
        N = N,
        cores = cores,
        splits = splits,
        verbose = TRUE,
        simulate.fast = TRUE
      )
  },
  N = 10000, cores = 1, splits = 1,
  # quick.test = function(f) f(N = 5, cores = 1,splits=1),
  depends.on = list(
    scenario.name, policy.name,
    paste0(scenario$region.points$region.name, collapse = "|")
  ),
  depend.on.function = FALSE,
  random.seed = 202202231356 %% 2^31
  )
  sim
}
```


```{r}
SIM.VERSION <- "sim_20220302_0849_25r_SCENARIO_METRICS"
names.TRIAL <- names(TRIAL)
# n <- n[stringr::str_starts(n,"D=5.V=10")]

GET.METRICS <- function(scenario.name, policy.name) {
  sim.name <- paste0(scenario.name, ".", policy.name)
  system(paste0("echo 'Computing metrics for ", sim.name, "'"))
  res <- run_experiment_inline(
    depend.on.function = FALSE,
    paste0(SIM.VERSION, "_", sim.name),
    function() {
      sim <- GET.SIM(scenario.name, policy.name)
      if (is.null(sim)) {
        return(NULL)
      }
      PARAMS <- list(
        default = DEFAULT.PARAMS
      )
      lapply(names(PARAMS), function(params.name) {
        params <- PARAMS[[params.name]]
        sim.with.params <- sim %>% with_params(params)
        sim.with.params %>%
          four_metrics_all() %>%
          mutate(
            scenario = !!scenario.name,
            policy = !!policy.name,
            params = !!params.name,
            .before = everything()
          )
      }) %>% bind_rows()
    }
  )
  if (!is.null(res)) {
    res %>%
      summarise(
        parse_dot_name(!!scenario.name) %>%
          rename_with(function(x) paste0("scenario.", x)),
        cur_data()
      )
  } else {
    NULL
  }
}
```
  
# Table 3.9 : The effect of including ("inc.low" column) an additional variable of low pwer in its own domain (σ=2, power=0.3) when all the existing variables have high power (σ=1, power 0.8).
(table_domain_n_vars_comb_all_domains_equal_inter_0.2_low_own.tex,
 table_domain_n_vars_comb_hierarchical_domains_inter_0.2_low_own.tex)

```{r} 
options(knitr.table.format = "latex")
library(kableExtra)
library(doParallel)
registerDoParallel(cores = 8)

format_round <- function(x, digits) format(round(x, digits), nsmall = digits)
format_range <- function(xs, digits, culprits = NULL, type) {
  if (type == "F") {
    paste0(
      format_round(max(xs), digits),
      " {\\footnotesize -", format_round(max(xs) - min(xs), digits), "}"
    )
  } else {
    paste0(
      format_round(min(xs), digits),
      " {\\footnotesize +", format_round(max(xs) - min(xs), digits), "}"
    )
  }
}
SCENARIO.METRICS.in_own_domain <-
  foreach(scenario.name = names.TRIAL, .combine = "bind_rows") %:%
  foreach(policy.name = names(POLICY), .combine = "bind_rows") %dopar% {
    data <- parse_dot_name(scenario.name)
    if (data$D <= 4 & data$`ρ` == 0.4 & data$`τ` == 0.2 &
      policy.name %in% c("all_domains_equal", "hierarchical_domains", "uni_adj") &
      !(data$D >= 2 & policy.name %in% c("uni_adj")) &
      data$extra %in% c("none", "in_own_domain")) {
      GET.METRICS(scenario.name, policy.name)
    } else {
      NULL
    }
  }

for (policy in c("all_domains_equal", "hierarchical_domains")) {
  for (`scenario.τ` in c(0.2)) {
    # for(scenario.vars in unique(SCENARIO.METRICS$scenario.vars)){
    for (params in c("default")) {
      df <- SCENARIO.METRICS.in_own_domain %>%
        # filter(scenario.vars == !!scenario.vars) %>%
        # filter(params   == !!params) %>%
        filter(policy == "all_domains_equal" & scenario.D == 2 & scenario.V %in% c(2, 4, 6, 8) |
          policy == "all_domains_equal" & scenario.D == 3 & scenario.V %in% c(3, 6, 9) |
          policy == "all_domains_equal" & scenario.D == 4 & scenario.V %in% c(4, 6, 9) |
          policy == "hierarchical_domains" & scenario.D == 3 & scenario.V %in% c(3, 6, 9) |
          policy == "hierarchical_domains" & scenario.D == 4 & scenario.V %in% c(4, 6, 9)) %>%
        filter(scenario.D <= 4) %>%
        filter(scenario.D > 1) %>%
        filter(!(scenario.D <= 2 & !!policy == "hierarchical_domains")) %>%
        filter((scenario.D == 1 & scenario.extra == "none" & policy == "uni_adj") |
          ((scenario.D >= 2 | scenario.extra == "in_own_domain") & policy == !!policy)) %>%
        filter(`scenario.τ` == !!`scenario.τ`) %>%
        filter(`scenario.ρ` == 0.4) %>%
        filter(params == !!params) %>%
        filter(scenario.extra %in% c("none", "in_own_domain")) %>%
        group_by(scenario.D, scenario.V, scenario.extra) %>%
        summarise(
          CSr.0    = format_range(CSr.stop.C, 2, culprits = scenario.Vd, type = "C"),
          FGr.LRV  = format_range(FGr.stop.A, 2, culprits = scenario.Vd, type = "F"),
          CGr.TV   = format_range(CGr.go.A, 2, culprits = scenario.Vd, type = "C")
          # FGr.TV1  = format_range(FGr.stop.D, 2, culprits=scenario.Vd, type="F"),
          # CGr.TV2  = format_range(CGr.go.B, 2, culprits=scenario.Vd, type="C")
        ) %>%
        ungroup() %>%
        arrange(scenario.D) %>%
        pivot_wider(values_from = c("CSr.0", "FGr.LRV", "CGr.TV"), names_from = scenario.extra, names_sep = ".")
      print(df)

      table <- kbl(df %>% mutate(
        scenario.D = NULL,
        V = scenario.V,
        scenario.V = NULL,
        .before = everything()
      ) %>%
        mutate(
          CSr.0.none = cell_spec(CSr.0.none, bold = df$CSr.0.none > df$CSr.0.in_own_domain, escape = F, format = "latex"),
          CSr.0.in_own_domain = cell_spec(CSr.0.in_own_domain, bold = df$CSr.0.none < df$CSr.0.in_own_domain, escape = F, format = "latex"),
          FGr.LRV.none = cell_spec(FGr.LRV.none, bold = df$FGr.LRV.none < df$FGr.LRV.in_own_domain, escape = F, format = "latex"),
          FGr.LRV.in_own_domain = cell_spec(FGr.LRV.in_own_domain, bold = df$FGr.LRV.none > df$FGr.LRV.in_own_domain, escape = F, format = "latex"),
          CGr.TV.none = cell_spec(CGr.TV.none, bold = df$CGr.TV.none > df$CGr.TV.in_own_domain, escape = F, format = "latex"),
          CGr.TV.in_own_domain = cell_spec(CGr.TV.in_own_domain, bold = df$CGr.TV.none < df$CGr.TV.in_own_domain, escape = F, format = "latex")
        ) %>%
        relocate( # "with.neg" = FGr.LRV.in_own_domain,
          V = V,
          "exc.low" = CSr.0.none,
          "inc.low" = CSr.0.in_own_domain,
          "exc.low  " = FGr.LRV.none,
          "inc.low  " = FGr.LRV.in_own_domain,
          "exc.low " = CGr.TV.none,
          "inc.low " = CGr.TV.in_own_domain
        ),
      "latex",
      booktabs = T, escape = FALSE
      )

      for (scenario.D in unique(df$scenario.D)) {
        table <- table %>% pack_rows(
          paste0("D=", scenario.D),
          min(which(df$scenario.D == scenario.D)),
          max(which(df$scenario.D == scenario.D))
        )
      }
      # table <- table %>% collapse_rows(columns = 1,  latex_hline = "major")
      table <- table %>% add_header_above(c(
        " " = 1, # "Parameters"=0,
        "$\\\\CSr$ at $\\\\downcone{\\\\vNoEffect}$" = 2,
        "$\\\\FGr$ at $\\\\downcone{\\\\vLRV}$" = 2,
        "$\\\\CGr$ at $\\\\upcone{\\\\vTV}$" = 2
      ), escape = F)
      table <- table %>% kable_styling(
        latex_options = "striped", position = "left" # ,
        # stripe_index = which(df$scenario.V %in% c(2,4,6,10))
      )
      table <- table %>% column_spec(c(3, 5), border_right = T)
      file.name <- paste0("report/table_domain_n_vars_comb_", policy, "_inter_", `scenario.τ`, "_low_own.tex")
      table %>% save_kable(file = file.name)
      cat(paste0(readLines(file.name)[1:7] %>% .[!is.na(.)], collapse = "\n"))
    }
  }
}
```

# Table 3.10: The inpact of including (inc.low column) an additional variable of low power (σ = 2, power = 0.3) in an existing domain when all the existing variables have high power (σ = 1, power 0.8).
(table_domain_n_vars_comb_all_domains_equal_inter_0.2_low_first_at_0LRVTV.tex,
 table_domain_n_vars_comb_hierarchical_domains_inter_0.2_low_first_at_0LRVTV.tex)

```{r} 
options(knitr.table.format = "latex")
library(kableExtra)

format_round <- function(x, digits) format(round(x, digits), nsmall = digits)
format_range <- function(xs, digits, culprits = NULL, type) {
  if (type == "F") {
    paste0(
      format_round(max(xs), digits),
      " {\\footnotesize -", format_round(max(xs) - min(xs), digits), "}"
    )
  } else {
    paste0(
      format_round(min(xs), digits),
      " {\\footnotesize +", format_round(max(xs) - min(xs), digits), "}"
    )
  }
}

SCENARIO.METRICS.in_first_domain <-
  foreach(scenario.name = names.TRIAL, .combine = "bind_rows") %:%
  foreach(policy.name = names(POLICY), .combine = "bind_rows") %dopar% {
    data <- parse_dot_name(scenario.name)
    if (data$D <= 5 & data$`ρ` == 0.4 & data$`τ` == 0.2 &
      !(data$D >= 2 & policy.name %in% c("uni_adj", "uni_adj_extra")) &
      data$extra %in% c("none", "in_first_domain")) {
      GET.METRICS(scenario.name, policy.name)
    } else {
      NULL
    }
  }

approach.suffix <- c("uni_adj")
for (policy in c("all_domains_equal", "hierarchical_domains")) {
  for (`scenario.τ` in c(0.2)) {
    # for(scenario.vars in unique(SCENARIO.METRICS$scenario.vars)){
    for (params in c("default")) {
      df <- SCENARIO.METRICS.in_first_domain %>%
        # filter(scenario.vars == !!scenario.vars) %>%
        # filter(params   == !!params) %>%
        filter(stringr::str_starts(policy, "all_domains_equal") & scenario.D == 2 & scenario.V %in% c(2, 4, 7) |
          stringr::str_starts(policy, "all_domains_equal") & scenario.D == 3 & scenario.V %in% c(3, 6, 9) |
          stringr::str_starts(policy, "all_domains_equal") & scenario.D == 4 & scenario.V %in% c(4, 7, 9) |
          stringr::str_starts(policy, "all_domains_equal") & scenario.D == 5 & scenario.V %in% c(5, 7, 9) |
          stringr::str_starts(policy, "hierarchical_domains") & scenario.D == 3 & scenario.V %in% c(3, 6, 9) |
          stringr::str_starts(policy, "hierarchical_domains") & scenario.D == 4 & scenario.V %in% c(4, 7, 9) |
          stringr::str_starts(policy, "hierarchical_domains") & scenario.D == 5 & scenario.V %in% c(5, 7, 9)) %>%
        filter(scenario.D > 1) %>%
        filter(scenario.D <= 5) %>%
        filter(!(scenario.D <= 2 & !!policy == "hierarchical_domains")) %>%
        filter(!(stringr::str_starts(scenario.Vd, "4"))) %>%
        filter((scenario.extra == "none" & ((scenario.D == 1 & policy == "uni_adj") |
          (scenario.D >= 2 & policy == !!policy))) |
          (scenario.extra == "in_first_domain" &
            ((scenario.D == 1 & policy %in% !!approach.suffix) |
              (scenario.D >= 2 & policy %in% paste0(!!policy, ".", !!approach.suffix))))) %>%
        mutate(policy.suffix = stringr::str_replace(pattern = paste0("^", !!policy, "\\.?"), replacement = "", string = policy)) %>%
        select(!policy) %>%
        filter(`scenario.τ` == !!`scenario.τ`) %>%
        filter(`scenario.ρ` == 0.4) %>%
        filter(params == !!params) %>%
        filter(scenario.extra %in% c("none", "in_first_domain")) %>%
        group_by(scenario.D, scenario.V, scenario.extra, policy.suffix) %>%
        summarise(
          CSr.0    = format_range(CSr.stop.C, 2, culprits = scenario.Vd, type = "C"),
          FGr.0    = format_range(FGr.stop.C, 2, culprits = scenario.Vd, type = "F"),
          FGr.LRV  = format_range(FGr.stop.A, 2, culprits = scenario.Vd, type = "F"),
          CGr.TV   = format_range(CGr.go.A, 2, culprits = scenario.Vd, type = "C")
          # FGr.TV1  = format_range(FGr.stop.D, 2, culprits=scenario.Vd, type="F"),
          # CGr.TV2  = format_range(CGr.go.B, 2, culprits=scenario.Vd, type="C")
        ) %>%
        ungroup() %>%
        group_by(scenario.D, scenario.V) %>%
        mutate(
          CSr.0.is.best    = CSr.0 == max(CSr.0) & !all(CSr.0 == max(CSr.0)),
          FGr.0.is.best    = FGr.0 == min(FGr.0) & !all(FGr.0 == min(FGr.0)),
          FGr.LRV.is.best  = FGr.LRV == min(FGr.LRV) & !all(FGr.LRV == min(FGr.LRV)),
          CGr.TV.is.best   = CGr.TV == max(CGr.TV) & !all(CGr.TV == max(CGr.TV))
          # FGr.TV1  = format_range(FGr.stop.D, 2, culprits=scenario.Vd, type="F"),
          # CGr.TV2  = format_range(CGr.go.B, 2, culprits=scenario.Vd, type="C")
        ) %>%
        rowwise() %>%
        mutate(
          CSr.0.cell = cell_spec(CSr.0, bold = CSr.0.is.best, escape = F, format = "latex"),
          FGr.0.cell = cell_spec(FGr.0, bold = FGr.0.is.best, escape = F, format = "latex"),
          FGr.LRV.cell = cell_spec(FGr.LRV, bold = FGr.LRV.is.best, escape = F, format = "latex"),
          CGr.TV.cell = cell_spec(CGr.TV, bold = CGr.TV.is.best, escape = F, format = "latex")
        ) %>%
        ungroup() %>%
        arrange(scenario.D) %>%
        pivot_wider(values_from = starts_with(c("CSr", "FGr", "CGr")), names_from = c("scenario.extra", "policy.suffix"), names_sep = ".")
      print(df)

      table3 <- kbl(df %>% transmute(
        V = scenario.V,
        "exc.low" = CSr.0.cell.none.,
        "inc.low" = CSr.0.cell.in_first_domain.uni_adj,
        "exc.low " = FGr.LRV.cell.none.,
        "inc.low " = FGr.LRV.cell.in_first_domain.uni_adj,
        "exc.low  " = CGr.TV.cell.none.,
        "inc.low  " = CGr.TV.cell.in_first_domain.uni_adj,
      ),
      "latex",
      booktabs = T, escape = FALSE
      )
      table3 <- table3 %>% add_header_above(c(
        " " = 1, # "Parameters"=0,
        "$\\\\CSr$ at $\\\\downcone{\\\\vNoEffect}$" = 2,
        "$\\\\FGr$ at $\\\\downcone{\\\\vLRV}$" = 2,
        "$\\\\CGr$ at $\\\\upcone{\\\\vTV}$" = 2
      ), escape = FALSE)

      for (combo in list( # list(file.suffix = "at_0", table = table1),
        # list(file.suffix = "at_LRVTV", table = table2),
        list(file.suffix = "at_0LRVTV", table = table3)
      )) {
        list2env(combo, environment())
        for (scenario.D in unique(df$scenario.D)) {
          table <- table %>% pack_rows(
            paste0("D=", scenario.D),
            min(which(df$scenario.D == scenario.D)),
            max(which(df$scenario.D == scenario.D))
          )
        }


        table <- table %>% kable_styling(
          latex_options = "striped", position = "left" # ,
          # stripe_index = which(df$scenario.V %in% c(2,4,6,10))
        )
        table <- table %>% column_spec(c(3, 5), border_right = T)
        file.name <- paste0("report/table_domain_n_vars_comb_", policy, "_inter_", `scenario.τ`, "_low_first_", file.suffix, ".tex")
        table %>% save_kable(file = file.name)
        cat(paste0(readLines(file.name)[1:7] %>% .[!is.na(.)], collapse = "\n"))
      }
    }
  }
}
```
