---
title: "Figures concerning rates"
output:
  pdf_document:
    latex_engine: xelatex
---

```{r, results= "hide", message=F, warning=F}
library(gonogo)
options(gonogo.experiment.dir = "_cache")
# devtools::load_all()
options(tikzMetricsDictionary = "_tikzMetrics")
options(tikzLatexPackages = c(
  "\\usepackage{tikz}\n",
  "\\usepackage[active,tightpage,psfixbb]{preview}\n",
  "\\PreviewEnvironment{pgfpicture}\n",
  "\\setlength\\PreviewBorder{0pt}\n",
  "\\usepackage{ulem}\n",
  "\\newcommand{\\downcone}{m}\n",
  "\\newcommand{\\upcone}{m}\n",
  "\\newcommand{\\vLRV}{LRV}\n",
  "\\newcommand{\\vTV}{TV}\n",
  "\\newcommand{\\vct}{}\n",
  "\\newcommand{\\RCGoNotFirstTV}{RCGoNRCGoNRCGoN}\n",
  "\\newcommand{\\vNoEffect}{0}\n",
  paste0(
    "\\newcommand{\\G",
    c("Ind", "IndAdj", "Hot", "Lik", "LikAdj", "Meas", "IndBon"),
    "}{mmmmm}"
  )
))
options(tikzDocumentDeclaration = "\\documentclass[10pt,onecolumn,english]{book}")
source("theme_pub.R")
```

```{r}
library(dplyr)
library(ggplot2)
library(tibble)
library(tidyr)
options(dplyr.summarise.inform = FALSE)
library(latex2exp)
# library(knitr)
library(kableExtra)
a <- 0
```


```{r}
TRIAL <- list()
for (n.per.group in c(17)) {
  for (n.domains in c(2, 3, 4, 5)) {
    # Maximum 10 variables, 4 variables per domain
    for (n.vars in c(n.domains, min(4 * n.domains, 10) - 1)) {
      # We skip these ones to save some computation
      for (domain.n.vars in generate_variable_groupings(
        n.domains,
        n.vars,
        min.vars.per.domain = 1,
        max.vars.per.domain = 4,
        ordered.except.for.first = 1
      )) {
        for (CORR in list(
          list(corr.intra = 0, corr.inter = 0),
          list(corr.intra = 0.4, corr.inter = 0.2)
        )) {
          list2env(CORR, environment())

          TRIAL[[paste0(
            "D=", n.domains,
            ".V=", n.vars,
            ".Vd=", paste(domain.n.vars, collapse = "_"),
            ".ρ=(", corr.intra, ")",
            ".τ=(", corr.inter, ")",
            ".N=", n.per.group,
            ".extra=none",
            ".unpowered=-1"
          )]] <-
            make_endpoints(
              n.domains = n.domains,
              domain.n.vars = domain.n.vars,
              corr.intra = corr.intra,
              corr.inter = corr.inter
            ) %>% with_n_patients(per.group = n.per.group)

          for (add.powerless in c(c(
            seq(from = 1, to = 3, by = 0.1),
            seq(from = 3, to = 12, by = 3),
            seq(from = 12, to = 20, by = 4)
          )) %>% unique()) {
            if (domain.n.vars[1] < 4) {
              TRIAL[[paste0(
                "D=", n.domains,
                ".V=", n.vars,
                ".Vd=", paste(domain.n.vars, collapse = "_"),
                ".ρ=(", corr.intra, ")",
                ".τ=(", corr.inter, ")",
                ".N=", n.per.group,
                ".extra=in_first_domain",
                ".unpowered=(", add.powerless, ")"
              )]] <-
                make_endpoints(
                  n.domains = n.domains,
                  domain.n.vars = {
                    dnv <- domain.n.vars
                    dnv[1] <- dnv[1] + 1
                    dnv
                  },
                  vars.sd = c(
                    rep(1, length.out = domain.n.vars[1]),
                    add.powerless,
                    rep(1, length.out = sum(domain.n.vars) - domain.n.vars[1])
                  ),
                  corr.intra = corr.intra,
                  corr.inter = corr.inter
                ) %>% with_n_patients(per.group = n.per.group)
            }

            if (n.domains < 5) {
              TRIAL[[paste0(
                "D=", n.domains,
                ".V=", n.vars,
                ".Vd=", paste(domain.n.vars, collapse = "_"),
                ".ρ=(", corr.intra, ")",
                ".τ=(", corr.inter, ")",
                ".N=", n.per.group,
                ".extra=in_own_domain",
                ".unpowered=(", add.powerless, ")"
              )]] <-
                make_endpoints(
                  n.domains = n.domains + 1,
                  domain.n.vars = c(domain.n.vars, 1),
                  vars.sd = c(rep(1, length.out = sum(domain.n.vars)), add.powerless),
                  corr.intra = corr.intra,
                  corr.inter = corr.inter
                ) %>% with_n_patients(per.group = n.per.group)
            }
          }
        }
      }
    }
  }
}

parse_dot_name <- function(name) {
  res <- stringr::str_match_all(name, "(([^.=]+)=([^().=]+|\\(([^)]+)\\)))*")[[1]]
  ii <- !is.na(res[, 3])
  res <- structure(
    coalesce(res[ii, 5], res[ii, 4]),
    names = res[ii, 3]
  ) %>% as.list()
  res <- lapply(res, function(v) {
    # if(stringr::str_detect(v, "^([0-9.]+_)*[0-9.]+$")) {
    if (stringr::str_detect(v, "^(-?[0-9.]+)$")) {
      n <- as.numeric(stringr::str_split(v, "_", simplify = TRUE))
      # if(length(n) > 1) list(n) else n
      n
    } else {
      v
    }
  }) %>% as_tibble_row()
  res$Vd <- as.character(res$Vd)
  res
}
TRIAL.space <- bind_rows(lapply(names(TRIAL), function(x) {
  bind_cols(
    tibble_row(trial.name = x),
    parse_dot_name(x)
  )
}))
TRIAL.space

a <- 0
```

```{r}

uni_adj <- make_schema_alias("uni_adj")
dealias.uni_adj <- function(...) {
  p_policy(
    stop.if = for_all_endpoints(p_univariate %>% has_stop()),
    go.if =
      at_least_1_adjusted(
        at_each_endpoint(p_univariate %>% has_go()),
        correction = "simes"
      )
  )
}

POLICY <- list(
  all_domains_equal =
    p_policy(
      stop.if =
        at_most_k(k = "z", at_each_domain(uni_adj %>% is_Go())),
      go.if =
        (at_least_k(k = "x", at_each_domain(uni_adj %>% is_Go())))
    ),
  hierarchical_domains =
    p_policy(
      stop.if =
        ((uni_adj %>% is_Stop()) %at_domain% "d1") %and%
          # 2 of the other domains are stop (3 including the first one)
          (at_least_k(k = 2, at_each_domain(uni_adj %>% is_Stop())) %at_domains% !"d1"),
      go.if =
        (((uni_adj %>% is_Go()) %at_domain% "d1") %or%
          # x of the other domains ~ x of all domains (otherwise the first condition holds)
          (at_least_k(k = "x", at_each_domain(uni_adj %>% is_Go())) %at_domains% !"d1")
        ) %and%
          none_of(at_each_endpoint(is_negatively_significant))
    )
)

a <- 0
```

```{r}
go.regions <- list(
  go.A     = effect_is_gt("tv") # ,
  # go.B     = (effect_is_gt("tv") %or% at_least_k(k=2,
  #                       at_each_domain(effect_is_gt("tv")))) %and%
  #   for_all_endpoints(effect_is_gt(0)),
  # go.C     = (at_least_k(k=2, at_each_domain(effect_is_gt("tv"))) %or% effect_is_gt("tv")) %and%
  #             for_all_endpoints(effect_is_gt(0)) %and%
  #              (effect_is_gt("tv")   %at_domain% "d1")
)
stop.regions <- list(
  stop.A   = effect_is_lt("lrv"),
  stop.C   = effect_is_lt(0) # ,
  # stop.H   = for_all_endpoints(effect_is_lt("lrv")) %and%
  #              (at_least_k(k=2, at_each_domain(effect_is_lt(0))) %or%  effect_is_lt(0)) %and%
  #                (effect_is_lt("0")   %at_domain% "d1")
)

DEFAULT.PARAMS <- list(
  "p.FS" = 0.1, "p.FG" = 0.2, "alpha" = 0.05,
  "x" = 2, "z" = 0
)
a <- 0
```

```{r}
SCENARIO.GET <- lapply(TRIAL, function(trial) {
  function() {
    make_scenario(
      trial = trial,
      go.regions = go.regions,
      stop.regions = stop.regions
    ) %>% expand_regions()
  }
})
a <- 0
```

```{r}
# policy <- schema %>% instantiate_at(scenario$trial$endpoints)
GET.SIM <- function(scenario.name, policy.name) {
  scenario <- SCENARIO.GET[[scenario.name]]()
  policy.schema <- POLICY[[policy.name]]
  sim.name <- paste0(scenario.name, ".policy=(", policy.name, ")")
  message(sim.name)
  run_experiment_inline(
    paste0("sim_20220315_1352_", sim.name),
    function(N, cores, splits) {
      scenario %>%
        simulate_with_policy(policy.schema,
          N = 10000,
          cores = 1,
          splits = 1,
          verbose = TRUE,
          simulate.fast = TRUE
        )
    },
    experiment.dir = "/scratch/kjmx773/gonogo-experiments",
    # quick.test = function(f) f(N = 5, cores = 1,splits=1),
    depend.on.function = FALSE
  )
}
a <- 0
```


```{r}
library(doParallel)
stopImplicitCluster()
options(mc.cores = 32, cores = 32)
registerDoParallel(makeForkCluster())

SCENARIO.DECISIONS.1 <-
  foreach(scenario.name = names(SCENARIO.GET), .combine = "bind_rows") %:%
  foreach(policy.name = names(POLICY), .combine = "bind_rows") %dopar% {
    sim.name <- paste0(scenario.name, ".", policy.name)
    system(paste0("echo '", sim.name, "'"))
    if (parse_dot_name(scenario.name)$D <= 2 &
      policy.name == "hierarchical_domains") {
      NULL
    } else {
      sim <- GET.SIM(scenario.name, policy.name)
      PARAMS <- list(
        default = DEFAULT.PARAMS
      )
      run_experiment_inline(
        paste0("sim_20220315_1352_agg_", sim.name),
        function() {
          lapply(names(PARAMS), function(params.name) {
            params <- PARAMS[[params.name]]
            sim.with.params <- sim %>% with_params(params)
            sim.with.params %>%
              aggregate_scenario() %>%
              .$decisions.per.effect %>%
              mutate(
                scenario = !!scenario.name,
                policy = !!policy.name,
                params = !!params.name,
                .before = everything()
              )
          }) %>% bind_rows()
        },
        depend.on.function = FALSE
      )
    }
  }

# print(SCENARIO.DECISIONS.1)

SCENARIO.DECISIONS <- SCENARIO.DECISIONS.1 %>%
  # select(!starts_with("effect.for."))%>%
  rowwise() %>%
  summarise(
    scenario.name = scenario,
    parse_dot_name(scenario) %>%
      rename_with(function(x) paste0("scenario.", x)),
    cur_data()
  ) %>%
  rowwise() %>%
  mutate(power.extra = {
    # print(scenario)
    if (scenario.extra == "none") {
      NA
    } else if (scenario.extra == "in_first_domain") {
      power_per_var(TRIAL[[scenario]])$vars$power[TRIAL[[scenario]]$endpoints$domains$n.vars[1]]
    } else if (scenario.extra == "in_own_domain") {
      power_per_var(TRIAL[[scenario]])$vars$power[n_vars(TRIAL[[scenario]])]
    } else {
      NULL
    }
  }) %>%
  ungroup()

# print(max(SCENARIO.METRICS$error.go.A,
#           SCENARIO.METRICS$error.go.B,
#           SCENARIO.METRICS$error.stop.A,
#           SCENARIO.METRICS$error.stop.B1,
#           SCENARIO.METRICS$error.stop.B2))

# SCENARIO.DECISIONS
a <- 0
```

# Figure 3.10 - Effect of adding a variable with lower power in its own domain when using the "all domains equal" policy
(power_analysis_all_domains_equal_in_own_domain.tex.fig)

# Figure 3.11 – Impact of adding a variable with lower power in its own domain when using the "hierarchical domains" policy
(power_analysis_hierarchical_domains_in_own_domain.tex.fig)

# Figure 3.12 - Effect of adding a variable with lower power into an existing domain when using the "all domains equal" policy
(power_analysis_all_domains_equal_in_own_domain.tex.fig)

# Figure 3.13 – Impact of adding a variable with lower power into the most important domain when using the "hierarchical domains" policy
(power_analysis_hierarchical_domains_in_own_domain.tex.fig)

```{r, fig.width=10,fig.height=11}

calculate_summaries <- function(x) {
  x %>%
    pivot_decisions_longer() %>%
    group_by(scenario.D, scenario.V, power.extra, effect.name, params, correct.decision, decision) %>%
    summarise(
      p.min = min(p),
      p.max = max(p),
      p.ref = {
        if (unique(correct.decision) == unique(decision)) {
          p.min
        } else {
          p.max
        }
      }
    ) %>%
    ungroup() %>%
    group_by(scenario.D, scenario.V, power.extra, effect.name, params) %>%
    mutate(p.bg = {
      # print(p.ref)
      ifelse(decision == "Discuss",
        1 - p.ref[decision == "Go"] - p.ref[decision == "Stop"],
        p.ref
      )
    }) %>%
    ungroup()
}

for (policy.name in # "all_domains_equal"
  names(POLICY)
) {
  for (scenario.extra in c(
    "in_first_domain",
    "in_own_domain"
  )) {
    dd <- SCENARIO.DECISIONS %>%
      filter(policy == !!policy.name)

    dd.e <- dd %>%
      filter(scenario.extra == !!scenario.extra) %>%
      filter(scenario.D %in% c(min(scenario.D), max(scenario.D)))

    dd.rR <- dd.e %>%
      # filter(scenario.D == min(scenario.D) | scenario.D == max(scenario.D)) %>%
      filter(`scenario.ρ` == 0.4 & `scenario.τ` == 0.2) %>%
      calculate_summaries()

    dd.rR.none <- dd %>%
      filter(scenario.extra == "none") %>%
      filter(scenario.Vd %in% dd.e$scenario.Vd) %>%
      # filter(scenario.D == min(scenario.D) | scenario.D == max(scenario.D)) %>%
      filter(`scenario.ρ` == 0.4 & `scenario.τ` == 0.2) %>%
      calculate_summaries()


    dd.rR.corr.0 <- dd.e %>%
      # filter(scenario.D == min(scenario.D) | scenario.D == max(scenario.D)) %>%
      filter(`scenario.ρ` == 0 & `scenario.τ` == 0) %>%
      calculate_summaries()

    dd.rR.none.corr.0 <- dd %>%
      filter(scenario.extra == "none") %>%
      filter(scenario.Vd %in% dd.e$scenario.Vd) %>%
      # filter(scenario.D == min(scenario.D) | scenario.D == max(scenario.D)) %>%
      filter(`scenario.ρ` == 0 & `scenario.τ` == 0) %>%
      calculate_summaries()


    # dd.r0 <- dd %>%
    #   filter(scenario.extra == !!scenario.extra) %>%
    #   filter(`scenario.ρ` == 0 & `scenario.τ` == 0)

    # dd.0.rR <- dd %>%
    #   filter(scenario.extra == !!scenario.extra) %>%
    #   filter(`scenario.ρ` == 0.4 & `scenario.τ` == 0.2)

    gg <- ggplot(dd.rR, aes(x = power.extra)) +
      facet_grid(scenario.D + scenario.V ~ effect.name,
        labeller =
          labeller(
            scenario.V = function(x) paste0("$\\nu = ", x, "$"),
            scenario.D = function(x) paste0("$\\delta  = ", x, "$"),
            effect.name = c(
              go.A.1 = "$\\vct{\\mu} = \\vTV$",
              stop.A.1 = "$\\vct{\\mu} = \\vLRV$",
              stop.C.1 = "$\\vct{\\mu} = \\vNoEffect$"
            )
          )
      ) +
      # Main area
      geom_area(aes(y = p.bg, fill = decision), alpha = 0.3) +
      geom_ribbon(
        data = dd.rR %>% filter(decision != "Discuss"),
        aes(
          ymin = ifelse(decision == "Go", 1 - p.min, p.min),
          ymax = ifelse(decision == "Go", 1 - p.max, p.max),
          fill = decision
        ),
        alpha = 0.5
      ) +
      geom_line(
        data = dd.rR %>% filter(decision != "Discuss"),
        aes(
          y = ifelse(decision == "Go", 1 - p.ref, p.ref),
          col = decision
        )
      ) +

      # Side column
      geom_col(data = dd.rR.none, aes(x = 1, y = p.bg, fill = decision), alpha = 0.3, width = 0.1) +
      geom_rect(
        data = dd.rR.none %>% filter(decision != "Discuss"),
        aes(
          ymin = ifelse(decision == "Go", 1 - p.min, p.min),
          ymax = ifelse(decision == "Go", 1 - p.max, p.max),
          xmin = 1 - 0.1 / 2,
          xmax = 1 + 0.1 / 2,
          fill = decision
        ),
        alpha = 0.5
      ) +
      geom_hline(
        data = dd.rR.none %>% filter(decision != "Discuss"),
        aes(
          yintercept = ifelse(decision == "Go", 1 - p.ref, p.ref),
          # yend = ifelse(decision=="Go",1-p.ref,p.ref),
          # x = 1-0.1/2,
          # xend = 1+0.1/2,
          linetype = "$V=\\nu$"
        ),
        col = "#222222"
      ) +
      geom_segment(
        data = dd.rR.none %>% filter(decision != "Discuss"),
        aes(
          y = ifelse(decision == "Go", 1 - p.ref, p.ref),
          yend = ifelse(decision == "Go", 1 - p.ref, p.ref),
          x = 1 - 0.1 / 2,
          xend = 1 + 0.1 / 2,
          col = decision
        )
      ) +

      # Corr 0
      # geom_area(aes(y = p.bg, fill=decision), alpha=0.2)+
      geom_line(
        data = dd.rR.corr.0 %>% filter(decision != "Discuss"),
        aes( # ymin = ifelse(decision=="Go",1-p.min,p.min),
          # ymax = ifelse(decision=="Go",1-p.max,p.max),
          y = ifelse(decision == "Go", 1 - p.ref, p.ref),
          linetype = "Corr. 0",
          group = decision,
          col = decision
        ),
        #      col="#222222"
      ) +
      geom_segment(
        data = dd.rR.none.corr.0 %>% filter(decision != "Discuss"),
        aes(
          y = ifelse(decision == "Go", 1 - p.ref, p.ref),
          yend = ifelse(decision == "Go", 1 - p.ref, p.ref),
          x = 1 - 0.1 / 2,
          xend = 1 + 0.1 / 2,
          linetype = "Corr. 0",
          col = decision
        ),
        #    col="#222222"
      ) +

      # Side column
      # geom_col(data = dd.rR.none, aes(x=1, y = p.bg, fill=decision), alpha=0.2, width=0.1)+
      # geom_rect(data = dd.rR.none %>% filter(decision != "Discuss"),
      #             aes(ymin = ifelse(decision=="Go",1-p.min,p.min),
      #                 ymax = ifelse(decision=="Go",1-p.max,p.max),
      #                 xmin = 1-0.1/2,
      #                 xmax = 1+0.1/2,
      #                 fill = decision),
      #             alpha = 0.4) +
      # geom_hline(data = dd.rR.none %>% filter(decision != "Discuss"),
      #            aes(yintercept = ifelse(decision=="Go",1-p.ref,p.ref),
      #                #yend = ifelse(decision=="Go",1-p.ref,p.ref),
      #                #x = 1-0.1/2,
      #                #xend = 1+0.1/2,
      #                linetype = "$V=\\nu$"),
      #                col="#222222") +
      #
      # geom_segment(data = dd.rR.none %>% filter(decision != "Discuss"),
      #            aes(y = ifelse(decision=="Go",1-p.ref,p.ref),
      #                yend = ifelse(decision=="Go",1-p.ref,p.ref),
      #                x = 1-0.1/2,
      #                xend = 1+0.1/2,
      #                col = decision)) +


      scale_y_continuous(
        labels = function(x) scales::percent(x, suffix = "\\%"), limits = c(0, 1),
        breaks = seq(0, 1, by = 0.2)
      ) +
      scale_x_continuous(
        breaks = c(seq(0, 0.8, by = 0.2), 1),
        labels = c(seq(0, 0.8, by = 0.2), "$-$")
      ) +
      labs(y = "", linetype = "Reference lines", x = "Power of extra variable", fill = "Decision", col = "Decision") +
      scale_color_Decision() +
      scale_fill_Decision() +
      theme_Publication() +
      scale_linetype_manual(
        values = c("dashed", "dotted"),
        labels = c(
          "$V=\\nu$" = "$(V=\\nu)$",
          "Corr. 0" = "$(\\rho=\\tau=0)$"
        )
      ) +
      theme(legend.box = "vertical") +
      theme()

    # print(gg)
    file.name <- paste0("report/power_analysis_", policy.name, "_", scenario.extra, ".tex.fig")
    tikzDevice::tikz(file = file.name, width = 4.8, height = 7.1)
    print(gg)
    dev.off()
  }
}
a <- 0
```


